Conservative Model Order Reduction for Fluid Flow

### 2018-10-10 sections/5.res.tex
Implement final corrections manuscript: add number of snapshots, briefly explain low pass filter on reduced modes, move the legends in figure 9

As centered schemes are often dissipation free, resolving the discontinuous initial data requires some artificial viscosity. In the high-fidelity model, the method discussed in \cite{artificial_dissipation} is used as an artificial viscosity. However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors.

The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$ over a period of $1$ time unit.

@@

The fully discrete skew-symmetric form \eqref{eq:3.27} is used for time integration over a time interval $[0,0.3]$. To resolve the discontinuous solution we use an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$.

@@

@@

@@

>>>>

As centered schemes are often dissipation free, resolving the discontinuous initial data requires some artificial viscosity. In the high-fidelity model, the method discussed in \cite{artificial_dissipation}\edit{, based on a derivative-based model,} is used as an artificial viscosity. However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors. \edit{The last $5\%$ of the POD modes are put to zero at each time iteration. The reason for the different treatment is that we want to avoid the reconstruction of the derivative of the solution in the full space during the integration of the reduced system.}

The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$ over a period of $1$ time unit.
\edit{A total of $500$ snapshots have been used for the computation of the basis in the offline stage.}

@@

The fully discrete skew-symmetric form \eqref{eq:3.27} is used for time integration over a time interval $[0,0.3]$. To resolve the discontinuous solution we use an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$. \edit{Regarding the reduction procedure, $1000$ snapshots of the numerical solution given by the high fidelity method have been collected.}

@@

\begin{subfigure}[t]{0.47\linewidth}

@@

                 %legend pos=south west,

@@

                 legend style={at={(axis cs:0.375,0.45)},anchor=south west},
